### 2017-06-27 README.Rmd
fleshed out simulate, added examples, and added stat = "prop"

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulation") %>% 
  calculate(stat = "prop") #
```

>>>>

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```
